### 2014-02-27 paper/formal.tex
more

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Using this definition, |specLang alpha (targetLang nop) = (ifc C, ifc
V, .->, erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and
$|ifc V| = |iS| \times |it|^*$, where $|it|^* \subset |it|$ it the
type for tasks whose expressions have been reduced to
values.\footnote{
  Here, we abuse notation by describing types for configuration parts using the
  same metavariables as the ``instance'' of the type, e.g., |it| for the type of
  task.
}
%
The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
containing |bullet|; Figure~\ref{fig:erasure} gives the precise definition for
our erasure function.
%
A task and its corresponding message queue is completely removed from the task
list if its label does not flow to the attacker observation level |il|;
otherwsie, we apply the erasure function homomorphically and remove any message
from the task's message queue that are more sensitive than |il|.

We note that the definition of |erasef il| precisely captures the IFC
language's attacker model.  For instance, in our case, by removing sensitive
tasks and messages from the system, we assume that that the attacker cannot
observe the number of sensitive tasks or messages.
%
%}

@@

\begin{definition}[$l$-equivalence]
    In a language |(C, .->, erasef l)|, two machine configurations
    |memberf (c, c') C| are considered $l$-equivalent (|c ~= c'|)
    if |erase l c = erase l c'|.
\end{definition}

>>>>

%{
%format .->  = "\overset{\alpha}{\hookrightarrow}"
Using this definition, |specLang alpha (targetLang nop) = (ifc C, ifc
V, .->, erasef il)|, such that $|ifc C| = |iS| \times \prod |it|$ and
$|ifc V| = |iS| \times |it|^*$, where $|it|^* \subset |it|$ it the
type for tasks whose expressions have been reduced to
values.\footnote{
  Here, we abuse notation by describing types for configuration parts using the
  same metavariables as the ``instance'' of the type, e.g., |it| for the type of
  task.
}
The erased configuration |tyerase (ifc C)| extends |ifc C| with configurations
containing |bullet|; Figure~\ref{fig:erasure} gives the precise definition for
our erasure function.
%
A task and its corresponding message queue is completely removed from the task
list if its label does not flow to the attacker observation level |il|;
otherwsie, we apply the erasure function homomorphically and remove any message
from the task's message queue that are more sensitive than |il|.
%}

@@

We note that the definition of |erasef il| precisely captures the IFC
language's attacker model. 
%
For instance, in our case, by removing sensitive tasks and messages from the
system, we assume that that the attacker cannot observe the number of sensitive
tasks or messages.
%
While such assumptions are standard~\tocite{}, our defintions allow for
stronger attackers that may be able to inspect resource usage.\footnote{
  We belive that we can extend |specLang alpha (targetLang nop)| to
  such models using the resource limits techniqes of~\tocite{}.
  %
  We leave this extension to future work.
}

Non-inteference relies on the defintion of an attacker's observational power at
security level |l|, which is typically defined as an equivalence
relation---called |l|-equivalence---on configurations, i.e., an attacker cannot
distinguish two configurations that are |l|-equivlaent.
%
Since our erasure function captures attacker mode, we simply define this
equivalance as the syntactic-equivalence of erased configurations.
%
\begin{definition}[|l|-equivalence]
    In a language |(C, .->, erasef l)|, two machine configurations
    |memberf (c, c') C| are considered $l$-equivalent (|c ~= c'|)
    if |erase l c = erase l c'|.
\end{definition}
%
